### 2021-10-08 paper/output/document/paper41.tex
me: i broke it irreparably and have been crying for the last week. nada: have you tried removing the line that says 2+2=5? me: good idea.

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
specified in the maxim. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.

@@

Given that the will function already excludes worlds where the circumstances fail (by rendering 
the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
that circumstances have on obligation. DDL has powerful axioms expressing the relationship between circumstances 
and obligation, such as the fact that obligations are monotonically increasing with respect to broader 
circumstances. Using the monadic obligation operator would require me to either operate with an empty 
notion of context or to redefine these axioms. The dyadic obligation operator lets me take advantage of the full 
power of DDL in expressing contrary-to-duty obligations. This is particularly important for Kantian ethics 
and the FUL specifically because many critiques of the FUL rely on attention to circumstances (tailoring 
objection) or lack thereof (ideal theory). This is also an innovation that my custom formalization presents 
over the prior work. By formally including the notion of a circumstance or context, I am able to represent 
these objections that Kantian scholars study. Formalizing Kantian ethics in a dyadic deontic logic 
instead of a monadic deontic logic is a key contribution of this thesis.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
when the subject does not act on it, the goal is not achieved.$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation} 
The former direction of the implication 
is intuitive: if the act results in the goal, it was effective in causing the goal. This represents `necessary'
causality.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
$M$ is no longer effective for $s$.%
}%
\begin{isamarkuptext}%
This formalizes Korgsaard's definition of the practical contradiction
interpretation:  a maxim is not universalizable 
if, in the world where the maxim becomes the standard practice (i.e. everyone acts on the maxim), the
agent's attempt to use the maxim's act to achieve the maxim's goal is frustrated. In other words, if 
the maxim is universally willed (captured by applying a universal qunatifier and the will function 
to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).

@@

It's not clear to me if there's any intuitive difference between these two representations, but the lemmas 
below (using simplified versions of the representations) show that my representation is weaker than 
the representation where the quantifier has larger scope. This seems promising—the representation in 
lemma test\_2 is likely too strong because the quantifier quantifies into $M a$ as well. It really 
doesn't seem like this should make a difference, since $p$ never appears on the RHS expression. Let's
see if Prof. Amin has insight.%

@@

@@

@@

@@

@@

@@

@@

%:%262=204%:%
%:%263=205%:%
%:%264=206%:%
%:%265=207%:%
%:%266=208%:%
%:%267=209%:%
%:%268=210%:%
%:%269=211%:%
%:%270=212%:%
%:%271=213%:%
%:%272=214%:%
%:%273=215%:%
%:%274=216%:%
%:%275=217%:%
%:%276=218%:%
%:%277=219%:%
%:%278=220%:%
%:%279=221%:%
%:%280=222%:%
%:%281=223%:%
%:%282=224%:%

>>>>

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
specified in the maxim. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.

@@

Given that the will function already excludes worlds where the circumstances fail (by rendering 
the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
that circumstances have on obligation. DDL has powerful axioms expressing the relationship between circumstances 
and obligation, such as the fact that obligations are monotonically increasing with respect to broader 
circumstances. Using the monadic obligation operator would require me to either operate with an empty 
notion of context or to redefine these axioms. The dyadic obligation operator lets me take advantage of the full 
power of DDL in expressing contrary-to-duty obligations. This is particularly important for Kantian ethics 
and the FUL specifically because many critiques of the FUL rely on attention to circumstances (tailoring 
objection) or lack thereof (ideal theory). This is also an innovation that my custom formalization presents 
over the prior work. By formally including the notion of a circumstance or context, I am able to represent 
these objections that Kantian scholars study. Formalizing Kantian ethics in a dyadic deontic logic 
instead of a monadic deontic logic is a key contribution of this thesis.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ \ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
%
\begin{isamarkuptext}%
A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
when the subject does not act on it, the goal is not achieved.$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation} 
The former direction of the implication 
is intuitive: if the act results in the goal, it was effective in causing the goal. This represents `necessary'
causality.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ LHS{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}LHS\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}LHS\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
$M$ is no longer effective for $s$.%
}\isanewline
\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
%
\begin{isamarkuptext}%
This formalizes Korgsaard's definition of the practical contradiction
interpretation:  a maxim is not universalizable 
if, in the world where the maxim becomes the standard practice (i.e. everyone acts on the maxim), the
agent's attempt to use the maxim's act to achieve the maxim's goal is frustrated. In other words, if 
the maxim is universally willed (captured by applying a universal qunatifier and the will function 
to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).

@@

It's not clear to me if there's any intuitive difference between these two representations, but the lemmas 
below (using simplified versions of the representations) show that my representation is weaker than 
the representation where the quantifier has larger scope. This seems promising—the representation in 
lemma test\_2 is likely too strong because the quantifier quantifies into $M a$ as well. It really 
doesn't seem like this should make a difference, since $p$ never appears on the RHS expression. Let's
see if Prof. Amin has insight.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ FUL{\isadigit{0}}{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}\ c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}{\isacharparenleft}O{\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This representation of the Formula of Universal Law reads, ``For all circumstances, goals, acts, 
and subjects, if the maxim of the subject performing the act for the goal in the circumstances is not 
universalizable (as defined above), then, at all worlds, in those circumstances, the subject 
is prohibited (obligated not to) from willing the maxim.

It's also inconsistent!!!! Boooooo%
}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymlongrightarrow}\ False{\isachardoublequoteclose}%

@@

\isacommand{using}\isamarkupfalse%
\ O{\isacharunderscore}diamond\ ax{\isacharunderscore}{\isadigit{5}}d\ \isanewline
\ \ \isacommand{using}\isamarkupfalse%
\ prod{\isachardot}simps{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ split{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%
\ fastforce%

@@

\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ imagine{\isacharunderscore}a{\isacharunderscore}world{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}imagine{\isacharunderscore}a{\isacharunderscore}world\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline

@@

\isamarkupcmt{The FUL really says, `imagine a world where the maxim were universalized...' I suspect that part of 
the problem with FUL0 is that it universalizes the maxim at the same world that prohibits it, which 
is weird because the agent performs the action (since it's universalized) but it's prohibited. Instead, 
we want to say that in some other world where the maxim is universalized, let's apply the universalizability 
test. This particular function represents a world where the maxim is universalized.%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ not{\isacharunderscore}contradictory{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}contradictory\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}c\ \isactrlbold {\isasymand}\ {\isacharparenleft}a\ p{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This function represents a maxim that is not contradictory, in that an agent can will it without 
contradiction. It's more of a sanity check.%
}\ \isanewline
\isanewline
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\ imagination{\isacharunderscore}works{\isacharcolon}{\isachardoublequoteopen}{\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ \ {\isacharparenleft}not{\isacharunderscore}contradictory\ M{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This axiom says, effectively, that our imagination works. In other words, for every maxim, if it 
isn't contradictory, there is some (imagined) world where it is universalized. This guarantees that the 
FUL can't be trivially true, since there is some world where the universalizability test is carried out.%
}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ True\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%

@@

\isacommand{by}\isamarkupfalse%
\ simp\ \isanewline

@@

\isamarkupcmt{Consistent so far:
Nitpick found a model for card i = 1 and card s = 1:

  Empty assignment%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ not{\isacharunderscore}vacuous{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}vacuous\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isasymnot}\ {\isacharparenleft}g\ {\isacharequal}\ c{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}a\ s\ {\isacharequal}\ c{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}not{\isacharunderscore}vacuous\ M\ s{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ M\ s{\isacharparenright}{\isacharbraceright}\ cw{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}FUL{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{$\color{blue}$ Nitpick found a counterexample for card s = 1 and card i = 1:

  Skolem constants:
    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
    c = ($\lambda x. \_$)($i_1$ := True)
    g = ($\lambda x. \_$)($i_1$ := False)
    $\lambda w$. p = ($\lambda x. \_$)($i_1$ := $s_1$)
    s = $s_1$ $\color{black}$%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\ FUL{\isacharcolon}FUL\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ True\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{$\color{blue}$ Nitpick found a model for card i = 1 and card s = 1:

  Empty assignment $\color{black}$%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This is a formulation of the FUL in which, assuming every maxim is universalized at some
world (this is the axiom imagination works), at that world (or other worlds like it), if the maxim is 
not effective for the agent, then it is prohibited at the current world cw. Couple of optimizations 
necessary to get Nitpick able to handle this:
(1) Couldn't use the effective and will functions becuase they made Nitpick time out. Is there a way 
to have a purely syntactic version of these functions? They'll make notation prettier? Like an 
abbreviation with free variables?

(2) If I quantify over the maxim's components, then Nitpick times out. If I specify a 
single maxim as a constant, then it can handle everything just fine. I could try, every 
time I'm working with an example, specifying properties of these constants. The downside is that if I want 
to work with 2 maxims at once, then I have to add more constants and add the FUL as an axiom again for each of these maxims. This might not 
be too annoying in practice (I don't think I'll need that many maxims), but there's something theoretically
unsatisfying about it. I guess one theoretical explanation is that the system can only handle small models?
Which is maybe not a huge problem?%

@@

%:%258=200%:%
%:%259=201%:%

@@

%:%262=203%:%
%:%263=204%:%
%:%265=205%:%
%:%266=206%:%
%:%267=206%:%
%:%268=207%:%
%:%271=209%:%
%:%272=210%:%
%:%273=211%:%
%:%274=212%:%
%:%275=213%:%
%:%276=214%:%
%:%277=215%:%
%:%278=216%:%
%:%279=217%:%
%:%280=218%:%
%:%281=219%:%
%:%282=220%:%
%:%283=221%:%
%:%284=222%:%
%:%285=223%:%
%:%286=224%:%
%:%287=225%:%
%:%288=226%:%
%:%289=227%:%
%:%290=228%:%
%:%291=229%:%
%:%292=230%:%
%:%293=231%:%
%:%295=234%:%
%:%296=234%:%
%:%298=235%:%
%:%299=236%:%
%:%300=237%:%
%:%301=238%:%
%:%302=239%:%
%:%303=240%:%
%:%304=240%:%
%:%305=241%:%
%:%306=242%:%
%:%307=242%:%
%:%309=242%:%
%:%313=242%:%
%:%314=242%:%
%:%315=243%:%
%:%316=243%:%
%:%317=243%:%
%:%324=243%:%
%:%325=244%:%
%:%326=245%:%
%:%327=245%:%
%:%328=246%:%
%:%330=247%:%
%:%331=248%:%
%:%332=249%:%
%:%333=250%:%
%:%334=251%:%
%:%335=251%:%
%:%336=252%:%
%:%337=253%:%
%:%338=253%:%
%:%339=254%:%
%:%341=255%:%
%:%342=256%:%
%:%343=256%:%
%:%344=257%:%
%:%345=258%:%
%:%346=258%:%
%:%348=259%:%
%:%349=260%:%
%:%350=261%:%
%:%351=261%:%
%:%352=262%:%
%:%353=263%:%
%:%354=263%:%
%:%355=264%:%
%:%356=264%:%
%:%358=264%:%
%:%362=264%:%
%:%363=264%:%
%:%365=265%:%
%:%366=266%:%
%:%367=267%:%
%:%368=268%:%
%:%376=268%:%
%:%377=269%:%
%:%378=270%:%
%:%379=270%:%
%:%380=271%:%
%:%381=272%:%
%:%382=273%:%
%:%383=273%:%
%:%384=274%:%
%:%385=275%:%
%:%386=275%:%
%:%387=276%:%
%:%388=276%:%
%:%390=276%:%
%:%394=276%:%
%:%395=276%:%
%:%397=277%:%
%:%398=278%:%
%:%399=279%:%
%:%400=280%:%
%:%401=281%:%
%:%402=282%:%
%:%403=283%:%
%:%404=284%:%
%:%412=284%:%
%:%413=285%:%
%:%414=286%:%
%:%415=286%:%
%:%416=287%:%
%:%417=288%:%
%:%418=288%:%
%:%419=289%:%
%:%420=289%:%
%:%422=289%:%
%:%426=289%:%
%:%427=289%:%
%:%429=290%:%
%:%430=291%:%
%:%431=292%:%
%:%441=294%:%
%:%442=295%:%
%:%443=296%:%
%:%444=297%:%
%:%445=298%:%
%:%446=299%:%
%:%447=300%:%
%:%448=301%:%
%:%449=302%:%
%:%450=303%:%
%:%451=304%:%
%:%452=305%:%
%:%453=306%:%
%:%454=307%:%
%:%455=308%:%
